%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Coinbase} % Organization
    {Bangalore, India} % Location
    {Nov 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for feature development and bug fixes on the Support section of Coinbase retail app (React native).}
        \item {Responsible for feature development and third party integrations for Support section of Coinbase website (React).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Development Engineer} % Job title
    {Agara} % Organization
    {Bangalore, India} % Location
    {Jan 2021 - Nov 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for the entire front end of the B2B SAAS platform of Agara (React.js).}
        \item {Developed entire onboarding flow on the UI of the app for the SAAS platform.}
        \item {Developed a canvas on the SAAS app for creating custom workflows for different use cases.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {Agara} % Organization
    {Bangalore, India} % Location
    {Sept 2019 - Jan 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed agent voice support UI with dashboard view of live calls which included live ML predictions on screen and case resolution flows (React.js).}
        \item {Responsible for email support UI with queue based dashboard for individual agents and case resoluton flows (React.js).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Baker Hughes} % Organization
    {Bangalore, India} % Location
    {Sept 2018 - Aug 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as a part of the Rule-Engine team which was responsible for creating rules for assets (sensors) and generating alerts based on events generated for those rules.}
        \item {Developed Rule-Updater microservice (Core Java) which was capable of updating rules based on threshold changes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Meredith Corp. (Time Inc.)} % Organization
    {Bangalore, India} % Location
    {July 2016 - Sept 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for building UI components (React.js) on a photo uploader tool which was built for editors of various Time Inc. brands to create and publish contests on the brand websites}
        \item {Responsible for implementing a real time trending system algorithm (MySQL stored procedures) for entire Time Inc. content.}
        \begin{itemize}
          \item{Team received Innovation Award in March 2017 from Time Inc. for this project.}
        \end{itemize}
        \item {Responsible for developing REST API endpoints (Java) for a video recommendation system for my team.}
        \begin{itemize}
          \item{Received Spot Award in December 2016 for this project.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
